Generality in food webs scales with species richness but not with latitude

### 2015-06-14 manuscript/latitudepaper.tex

\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

\title{Generality in food webs scales with species richness but not with latitude}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
\date{$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand}
\medskip$^2$Department of Biology\\Life Science Centre\\
Dalhousie University\\1355 Oxford St.\\P0 BOX 15000\\
Halifax, NS B3H 4R2\\Canada\\}

\begin{document}
\maketitle
\baselineskip=8.5mm

\vspace{0.4 in}

\section*{Abstract}

>>>>

\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm
\begin{document}

\title{Generality in food webs scales with species richness but not with latitude}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
\date{$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand \\
\medskip$^2$Department of Biology\\
Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
Halifax NS, B3H 4R2\\ Canada\\}

\maketitle
\baselineskip=8.5mm

\vspace{0.3 in}

\begin{spacing}{1.0}
\section*{Abstract}
